Acceleration of plague outbreaks in the second pandemic

### 2020-07-14 supp.Rnw
change .crop to _crop
New submission pipeline
avoid warning in supp

%% we need to cross-reference to main manuscript file:
\usepackage{xr-hyper}
\externaldocument{ms}

@@

In the idealized situation in which the generation interval is exponentially distributed (as in the standard SIR model) then \cite{WallLips07}, as mentioned in the Discussion in the main text, 
%
\begin{linenomath*}
\begin{equation}\label{E:rofR}
r = \frac{\R_0-1}\gentime \,,
\end{equation}
\end{linenomath*}
%
where $\gentime$ is the mean generation interval.  Consequently, if this simple relationship holds and the mean generation interval \emph{does not change}, then a change in growth rate $r_1\to r_2$ implies a change in basic reproduction number $\R_{0,1}\to\R_{0,2}$, where
%
\begin{linenomath*}
\begin{equation}\label{E:1to2}
\frac{\R_{0,2}}{\R_{0,1}} = \frac{r_2\gentime+1}{r_1\gentime+1} \,.
\end{equation}
\end{linenomath*}
%
If we assume the estimate of $\gentime=18$ days obtained
\hyperlink{sec:gentime}{above}, and the MLE growth rates from early and late wills
listed in \cref{tab:params}, the relative change in reproduction
number that needs explanation is
<<rat_R0_calc,echo=FALSE>>=
ratR0 <- function(r){ (r / 365 * 18) + 1 }
load("analysis/fits/epochsum.RData")
r1 <- rvals["fit","early"]
r2 <- rvals["fit","late"]
R01 <- ratR0(r1)
R02 <- ratR0(r2)
R0ratio <- R02/R01
@ 
%
\begin{linenomath*}
\begin{equation}\label{E:Rratio}
\frac{\R_{0,2}}{\R_{0,1}} 
\approx
\frac
{\Sexpr{round(r2,1)} \cdot \frac{18}{365} + 1}
{ \Sexpr{round(r1,2)} \cdot \frac{18}{365} + 1}
\approx
\frac{\Sexpr{round(R02,2)}}{\Sexpr{round(R01,2)}} 
\approx \Sexpr{round(R0ratio,2)}
\,.
\end{equation}
\end{linenomath*}
%
where the second subscript (1 or 2) denotes the early or late epoch, respectively.

@@

\newcommand{\mywidth}{\textwidth}
%
\begin{figure*}%[h!]
\begin{center}
\includegraphics[width=\mywidth]{analysis/plots/plotallscaled.crop.pdf}
\end{center}
\caption[Plague deaths per 1000 per week]{Plague deaths per 1000 persons per week, from 1563 to 1666.
Epidemics that exceeded 5 on this scale were classified as \emph{major}.
Analysis of the major epidemics is shown in \cref{tab:params,F:timeseries,F:combdata}.  Corresponding analyses of all of the minor epidemics are presented
in \cref{tab:minorparams,F:seasonalgrowth}.
}
\label{F:all1600s.scaled}
\end{figure*}
%

\begin{figure*}%[h!]
\begin{center}
%%\scalebox{0.6}{
\includegraphics[width=\mywidth]{analysis/plots/plotall.crop.pdf}
%%}
\end{center}
\caption[Plague deaths]{All plague deaths reported in London from 1563 to 1666.}
\label{F:all1600s}
\end{figure*}
%

>>>>

%% we need to cross-reference to main manuscript file:
\usepackage{xr-hyper}
\usepackage{grffile}
\externaldocument{ms}

@@

In the idealized situation in which the generation interval is exponentially distributed (as in the standard SIR model) then \cite{WallLips07}, as mentioned in the Discussion in the main text, 
%
\begin{linenomath*}
\begin{equation}\label{E:rofR}
r = \frac{\R_0-1}\gentime \,,
\end{equation}
\end{linenomath*}
%
where $\gentime$ is the mean generation interval.  Consequently, if this simple relationship holds and the mean generation interval \emph{does not change}, then a change in growth rate $r_1\to r_2$ implies a change in basic reproduction number $\R_{0,1}\to\R_{0,2}$, where
%
\begin{linenomath*}
\begin{equation}\label{E:1to2}
\frac{\R_{0,2}}{\R_{0,1}} = \frac{r_2\gentime+1}{r_1\gentime+1} \,.
\end{equation}
\end{linenomath*}
%
If we assume the estimate of $\gentime=18$ days obtained
\hyperlink{sec:gentime}{above}, and the MLE growth rates from early and late wills
listed in \cref{tab:params}, the relative change in reproduction
number that needs explanation is
<<rat_R0_calc,echo=FALSE,warning=FALSE>>=
ratR0 <- function(r){ (r / 365 * 18) + 1 }
load("analysis/fits/epochsum.RData")
r1 <- rvals["fit","early"]
r2 <- rvals["fit","late"]
R01 <- ratR0(r1)
R02 <- ratR0(r2)
R0ratio <- R02/R01
@ 
%
\begin{linenomath*}
\begin{equation}\label{E:Rratio}
\frac{\R_{0,2}}{\R_{0,1}} 
\approx
\frac
{\Sexpr{round(r2,1)} \cdot \frac{18}{365} + 1}
{ \Sexpr{round(r1,2)} \cdot \frac{18}{365} + 1}
\approx
\frac{\Sexpr{round(R02,2)}}{\Sexpr{round(R01,2)}} 
\approx \Sexpr{round(R0ratio,2)}
\,.
\end{equation}
\end{linenomath*}
%
where the second subscript (1 or 2) denotes the early or late epoch, respectively.

@@

\newcommand{\mywidth}{\textwidth}
%
\begin{figure*}%[h!]
\begin{center}
\includegraphics[width=\mywidth]{analysis/plots/plotallscaled_crop.pdf}
\end{center}
\caption[Plague deaths per 1000 per week]{Plague deaths per 1000 persons per week, from 1563 to 1666.
Epidemics that exceeded 5 on this scale were classified as \emph{major}.
Analysis of the major epidemics is shown in \cref{tab:params,F:timeseries,F:combdata}.  Corresponding analyses of all of the minor epidemics are presented
in \cref{tab:minorparams,F:seasonalgrowth}.
}
\label{F:all1600s.scaled}
\end{figure*}
%

\begin{figure*}%[h!]
\begin{center}
%%\scalebox{0.6}{
\includegraphics[width=\mywidth]{analysis/plots/plotall_crop.pdf}
%%}
\end{center}
\caption[Plague deaths]{All plague deaths reported in London from 1563 to 1666.}
\label{F:all1600s}
\end{figure*}
%
